Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-04 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text and code

\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to program verification. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected by our automated verification method.
\end{abstract}

@@

\section{Introduction}
There are presently 1 billion people with no access to electricity worldwide~\cite{Coelho}. 
%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
%
%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}.

@@

%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
Using the maximum power point current (cf. ~\eqref{eq:Imfinal}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor is determined by ~\eqref{eq:a}:
\begin{equation}
\label{eq:a}
a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) },
\end{equation}

@@

The PV generator model is now completely determined. It requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers.
%
%If the PV cells are in parallel, then there is a parallel array. Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
%
%\begin{equation}
%\label{eq:Iarray}
%I_{array} = (N_{cells in parallel})(I_{one cell})
%\end{equation}
%
%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
%
%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
%
%\begin{equation}
%\label{eq:Varray}
%V_{array} = (N_{cells in series})(V_{one panel})
%\end{equation}
%
%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
%------------------------------------------------------------
\subsection{The Battery Storage Model }
\label{sec:BATmodel}
%------------------------------------------------------------

@@

%The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. %MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power. Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 

@@

To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \textunderscore off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}. PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $. 
%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
%\includegraphics[width=0.4\textwidth]{controllerover}
%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
%\label{fig:controllerover}
In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \textunderscore off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}. The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \textunderscore on}$.
%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
%\includegraphics[width=0.4\textwidth]{controllerdisc}
%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
%\label{fig:controllerdisc}
%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.

@@

%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model). 
%
%--------------------------------------------------
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%--------------------------------------------------
%It is necessary to keep in mind that 
Validation is the process of determining whether a design meets the user requirements, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}. If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate the verification process, thus resulting in a process known as \textit{formal verification}. Verification may form part of a validation process.
%, but in general, validation cannot be formalized because it relates a system design to intent.  
While simulation and testing explore some of the possible behaviors and scenarios of the system, leaving open the question of whether the unexplored trajectories may contain a flaw, formal verification conducts an exhaustive exploration of all possible behaviors. Thus, when a design is pronounced correct by a formal verification method, it implies that all behaviors have been explored, and the questions of adequate coverage or a missed behavior becomes irrelevant \cite{Clarke2012}.
%Simulation may also be used for validation, but it is more problematic for verification.
%In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs. Testing can also be used for validation, however it is not feasible to cover all the aspects of the design space, and some times the real system must be used instead of a computing model.
 %

@@

%-------------------------------------
\section{Conclusion and Future Work}
\label{sec:Conclusions}
%-------------------------------------
We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W. Although this verification method takes longer than simulation methods, it is able to find specific conditions that lead to failures in a PV system previously validated by a commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail. 
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems. We will also consider other types of renewable energy and even hybrid ones to allow our method to design and verify typical rural electrification.
%
%It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results. The proposed tool was successful in find sizing errors and to indicate in which conditions a PV system can fails.
% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements. 
%
%Plus (need to think about it): verification in every-hour of a 48h cycle?, PV model math model can be improved, charge/discharge of batteries can be improved (is a simplified model), house's power consumption is not flat or constant, the dweller can buy more home appliances, synthesis need a data base of components, to test peak (surge) consumption (above the nominal), additional models for on-grid/off-grid farm, hybrid, and on-grid with batteries).
% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed
% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%
%\appendices
%\section{Proof of the First Zonklar Equation}
%Appendix one text goes here.
% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section{}
%Appendix two text goes here.
% use section* for acknowledgment
\section*{Acknowledgments}
The authors would like to thank Coventry University for the availability of the case studies (real PV systems) to validate the tool and to support the mobility of one researcher to UK.

>>>>

\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to any kind of program verification. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated as well. Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
\end{abstract}

@@

\section{Introduction}
Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}. The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}. Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}. Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities.

In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.

%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
%
%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}. However, this growth is not driven by isolated systems.

@@

%The ideality (or quality) factor of the diode $ a $, which is usually considered as a constant \cite{Villalva}, is determined in the reference state. 
Using the maximum power point current (cf. ~\eqref{eq:Imfinal}) and the saturation current in the reference temperature given by ~\eqref{eq:I0}, the diode ideality factor~\cite{Saloux} is determined by ~\eqref{eq:a}:
\begin{equation}
\label{eq:a}
a = \dfrac{q(V_{m,ref}-V_{oc,ref})}{Nk_{B}T} \dfrac{1}{ln \left( 1 - \dfrac{I_{m,ref}}{I_{sc,ref}}  \right) },
\end{equation}

@@

The PV generator model is now completely determined; it requires the actual cell temperature (or the air temperature), the actual solar irradiance and common data provided by manufacturers in data-sheets or manuals.
%
%If the PV cells are in parallel, then there is a parallel array. Therefore, there will be a change at the $ I_{ph} $ and $ I_{0} $and the resulting current is given by Equation \ref{eq:Iarray}, as demonstrated in \cite{Saloux}.
%
%\begin{equation}
%\label{eq:Iarray}
%I_{array} = (N_{cells in parallel})(I_{one cell})
%\end{equation}
%
%Where $ I_{one cell} $ is the current from Equation \ref{eq:Imfinal}.
%
%In addition, if the panels are in series, the current do not change but the total voltage is the sum of the each panel's voltage.
%
%\begin{equation}
%\label{eq:Varray}
%V_{array} = (N_{cells in series})(V_{one panel})
%\end{equation}
%
%Where $ V_{one panel} $ is the voltage from Equation \ref{eq:Vmfinal}.
%------------------------------------------------------------
\subsection{The Battery Storage Model }
\label{sec:BATmodel}
%------------------------------------------------------------

@@

The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power. Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 

@@

To protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $V_{max \textunderscore off}$ and when the current required by the load is less than the current delivered by the PV arrays~\cite{Hansen}. PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $. 
%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{controllerover}
%\centering
%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
%\label{fig:controllerover}
%\end{figure}
%
In order to protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $V_{min \textunderscore off}$ and when the current required by the load is larger than the current delivered by the PV arrays~\cite{Hansen}. The load is reconnected to the system, when the terminal voltage is above a certain value $V_{min \textunderscore on}$.
%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{controllerdisc}
%\centering
%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
%\label{fig:controllerdisc}
%\end{figure}
%
%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
%
The steps in the modeling of the controller process are summarized in Table~\ref{table:controller}.

@@

%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model). 
%
%
%--------------------------------------------------
\section{Verification of the PV Project Sizing}
%--------------------------------------------------
In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a. sizing check).
%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.

Therefore this is a additional feature included at this paper. The sizing check will be performed, as proposed at the methodology, and the tool will indicate if there is an error of sizing before to perform the automated verification of the system. This stage ensures that the system meets the standard project steps related to the critical design month~\cite{Pinho}.
%
Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

The total minimum number of needed solar panels ($N_{TPmin}$) is computed by ~\eqref{eq:NTPmin} and the check is performed using ~\eqref{eq:NTP}, where the sized number of panels ($ N_{TP} $) must be greater than the result from ~\eqref{eq:NTPmin}.
\begin{equation}
\label{eq:NTPmin}
N_{TPmin} = \dfrac{E_{corrected}}{E_{p}}.
\end{equation}

\begin{equation}
\label{eq:NTP}
N_{TP} \geq N_{TPmin}.
\end{equation}

Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively. With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}), $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
\begin{equation}
\label{eq:NPSmin}
N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}.
\end{equation}

\begin{equation}
\label{eq:NPPmin}
N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}.
\end{equation}

\begin{equation}
\label{eq:NPS}
N_{PS} \geq N_{PSmin}.
\end{equation}

\begin{equation}
\label{eq:NPP}
N_{PP} \geq N_{PPmin}.
\end{equation}

Related to the batteries, firstly must be defined the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
\begin{equation}
\label{eq:Cbank}
C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}.
\end{equation}
%
\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
%
Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}. Additionally, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
\begin{equation}
\label{eq:Nbtotal}
N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}.
\end{equation}

\begin{equation}
\label{eq:batcheck}
\left( N_{BS} \times  N_{BP} \right) \geq N_{B}total.
\end{equation}

Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem}: 
\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}.
\end{equation}

Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
%
\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right]. 
\end{equation}

The controller must meet the maximum current from the PV array given by \eqref{eq:icmin} and \eqref{eq:icicmin}.
\begin{equation}
\label{eq:icmin}
I_{c,min} = I_{sc,amb} \times N_{PP}.
\end{equation}

\begin{equation}
\label{eq:icicmin}
I_{c} \geq I_{c,min}.
\end{equation}

The sizing project check of the inverter is carried out by means of three equations. Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
%
\begin{equation}
\label{eq:vindc} 
V_{in}DC = V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
V_{out}AC = V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}

Worth to mention that the charge controller, the battery, and the inverter have a nominal efficiency presented at data sheets, and those numbers are very close to 100\%. However, based on empirical data, those efficiencies must be corrected, according to the loading of each component. If field or essay data is not available, considering that the proposed tools is aimed to be used prior the deployment of the PV system at the field, it is recommended (at least) to correct the battery efficiency ($\eta_{b}$) to 85\%.
%
%--------------------------------------------------
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%--------------------------------------------------
%It is necessary to keep in mind that 
Validation is the process of determining whether a design meets the user requirements, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}. If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate the verification process, thus resulting in a process known as \textit{formal verification}. Verification may form part of a validation process.
%, but in general, validation cannot be formalized because it relates a system design to intent.  
While simulation and testing explore some of the possible behaviors and scenarios of the system, leaving open the question of whether the unexplored trajectories may contain a flaw, formal verification conducts an exhaustive exploration of all possible behaviors. Thus, when a design is pronounced correct by a formal verification method, it implies that all behaviors have been explored, and the questions of adequate coverage or a missed behavior becomes irrelevant \cite{Clarke2012}.
%Simulation may also be used for validation, but it is more problematic for verification.
%In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs. Testing can also be used for validation, however it is not feasible to cover all the aspects of the design space, and some times the real system must be used instead of a computing model.
 %

@@

%-------------------------------------
\section{Conclusions and Future Work}
\label{sec:Conclusions}
%-------------------------------------
We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W. Although this verification method takes longer than simulation methods, it is able to find specific conditions that lead to failures in a PV system previously validated by a commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail. 
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found, thus leading to an optimum sizing of PV systems. We will also consider other types of renewable energy and even hybrid ones to allow our method to design and verify typical rural electrification.
%
%It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results. The proposed tool was successful in find sizing errors and to indicate in which conditions a PV system can fails.
% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements. 
%
%Plus (need to think about it): verification in every-hour of a 48h cycle?, PV model math model can be improved, charge/discharge of batteries can be improved (is a simplified model), house's power consumption is not flat or constant, the dweller can buy more home appliances, synthesis need a data base of components, to test peak (surge) consumption (above the nominal), additional models for on-grid/off-grid farm, hybrid, and on-grid with batteries).
% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed
% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%
%\appendices
%\section{Proof of the First Zonklar Equation}
%Appendix one text goes here.
% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section{}
%Appendix two text goes here.
% use section* for acknowledgment
\section*{Acknowledgments}
The authors would like to thank Coventry University for the availability of the case studies (real PV systems) to validate the tool and to support the mobility of one researcher to UK.
